Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-02-17 article/Article.tex
article continuated

@@

% Example of reconstruction of a discrete squares with various orientations
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=8cm]{images/perimRotatedSquares}
\includegraphics[width=8cm]{images/errorRotatedSquares}
\end{center}
\caption{Variations of perimeter measure of a digitized square depending on the orientation. 
Left: perimeter measures. Right: relative errors (in percent).}
\label{fig:MeasureSquareOriented}
\end{figure}

@@

\begin{table}[!htb]
\begin{center}\begin{tabular}{ccccccc}
shape	& $(\varphi,\theta)$ & $S$ 	& $S_{crofton^3}$ & $S_{crofton^{13}}$ & $S_{isosurface}$ \tabularnewline \hline 
ball 		& $n.a.$  		& 	$11309.8$	& $11312.0$ 	& $11306.6$ 	& $12253.9$ 	\tabularnewline 
prolate	& $( 0,  0)$  	& 	$3082.9$ 	& $2938.7$ 	& $3084.6$ 	& $3344.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $3137.3$ 	& $3086.3$ 	& $3340.6$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $3150.6$ 	& $3083.3$ 	& $3337.8$ 	\tabularnewline
oblate 	& $( 0,  0)$  	& 	$6856.8$ 	& $6290.7$ 	& $6807.6$ 	& $7387.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $6872.0$ 	& $6789.0$ 	& $7346.2$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $7154.7$ 	& $6808.5$ 	& $7366.1$ 	\tabularnewline
torus 		& $( 0,  0)$  	& 	$11843.5$	& $11417.3$ 	& $11792.9$ 	& $12785.4$ 	\tabularnewline
-			& $(45,  0)$  	& 	$-$    	& $11809.3$ 	& $11766.8$ 	& $12844.4$ 	\tabularnewline
- 			& $(45, 45)$ 	& 	$-$ 	 	& $12086.0$ 	& $11822.4$ 	& $12798.4$ 	\tabularnewline
\end{tabular}\end{center}
\caption{ \label{tab:CompareSurfaceArea}
Differences between actual surface area and its measures with different methods, 
on shapes with various orientations.
The orientation is given by the direction of the shape rotation axis, defined by 
the azimut $\varphi$ (between 0 and 360 degrees) and the colatitude $\theta$ (between 0 and 180 degrees).}
\end{table}

% \section{Timing}
% [c'est rapide]

>>>>

\let\oldtabular=\tabular
\def\tabular{\small\oldtabular}

@@

% Example of reconstruction of a discrete squares with various orientations
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=8cm]{images/perimRotatedEllipses}
\includegraphics[width=8cm]{images/errorRotatedEllipses}
\end{center}
\caption{Variations of perimeter measure of a digitized ellipse depending on the orientation. 
Left: perimeter measures. Right: relative errors (in percent).}
\label{fig:MeasureSquareOriented}
\end{figure}

@@

\begin{table}[!htb]
\begin{center}\begin{tabular}{ccccccc}
Shape      & $(\varphi,\theta)$ & $S$            & $S_{crofton^3}$     & $S_{crofton^{13}}$  & $S_{VTKmarch}$       & $S_{ITKiso}$  \tabularnewline
\hline 
\hline 
ball       & $n.a.$             &     $11309.8$  & $11312.0\ (+0.0\%)$ & $11306.6\ (-0.0\%)$ & $12298.2\ (+8.7\%)$  & $12299.5\ (+8.8\%)$ \tabularnewline 
prolate    & $( 0,  0)$         &     $3082.9$   & $2938.7\ (-4.7\%)$  & $3084.6\ (+0.1\%)$  & $3354.1\ (+8.8\%)$   & $3354.9\ (+8.8\%)$  \tabularnewline
-          & $(45,  0)$         &     $-$        & $3137.3\ (+1.8\%)$  & $3086.3\ (+0.1\%)$  & $3353.9\ (+8.8\%)$   & $3354.7\ (+8.8\%)$  \tabularnewline
-          & $(45, 45)$         &     $-$        & $3150.6\ (+2.2\%)$  & $3083.3\ (+0.0\%)$  & $3351.5\ (+8.7\%)$   & $3352.2\ (+8.7\%)$  \tabularnewline
oblate     & $( 0,  0)$         &     $6856.8$   & $6290.7\ (-8.3\%)$  & $6807.6\ (-0.7\%)$  & $7410.2\ (+8.1\%)$   & $7411.3\ (+8.1\%)$  \tabularnewline
-          & $(45,  0)$         &     $-$        & $6872.0\ (+0.2\%)$  & $6789.0\ (-1.0\%)$  & $7369.7\ (+7.5\%)$   & $7370.7\ (+7.5\%)$  \tabularnewline
-          & $(45, 45)$         &     $-$        & $7154.7\ (+4.3\%)$  & $6808.5\ (-0.7\%)$  & $7385.9\ (+7.7\%)$   & $7386.7\ (+7.7\%)$  \tabularnewline
torus      & $( 0,  0)$         &     $11843.5$  & $11417.3\ (-3.6\%)$ & $11792.9\ (-0.4\%)$ & $12826.6\ (+8.3\%)$  & $12828.7\ (+8.3\%)$ \tabularnewline
-          & $(45,  0)$         &     $-$        & $11809.3\ (-0.3\%)$ & $11766.8\ (-0.6\%)$ & $12787.4\ (+8.0\%)$  & $12789.3\ (+8.0\%)$ \tabularnewline
-          & $(45, 45)$         &     $-$        & $12086.0\ (+1.9\%)$ & $11822.4\ (-0.2\%)$ & $12849.1\ (+8.5\%)$  & $12851.1\ (+8.5\%)$ \tabularnewline
\hline 
\end{tabular}\end{center}
\caption{ \label{tab:CompareSurfaceArea}
Differences between actual surface area and its measures with different methods, 
on shapes with various orientations.
The orientation is given by the direction of the shape rotation axis, defined by 
the azimut $\varphi$ (between 0 and 360 degrees) and the colatitude $\theta$ (between 0 and 180 degrees).}
\end{table}

\section{Timing}

The performance of the Crofton based method as well as several other methods available in ITK or VTK
are shown in Table~\ref{tab:perf}. The timings were obtained using the {\tt
./perf3D ../images/ball450.nrrd} command on an Intel(R) Xeon(R) CPU X5570 processor at 2.93GHz
with 8192Kb cache, 24Gb of RAM running Ubuntu linux 11.04 64 bits with gcc 4.5.2.
The input image have a size of $1000 \times 1000 \times 1000$ and contains a single binary object:
a ball of radius 450.

%./marchingCubes ../images/ball450.nrrd
% Tcroft    Tmarch    Tmarch2    Timesh    speedupMarch    speedupMarch2    speedupIMesh    Scroft    Smarch    Smarch2    Simesh    %march    %march2    %imesh    fname    
% 1.80882    26.6482    15.3972    29.1124    14.7324    8.51231    16.0947    2.32339e+06    2.33467e+06    2.52777e+06    2.52779e+06    0.483298    8.08555    8.08621    ../images/ball450.nrrd

\begin{table}[!htb]
\begin{center}\begin{tabular}{cc}
Method                                   & Timing \\
 \hline 
 \hline
Proposed method                          & 1.80882 \\
VTK marching cubes                       & 15.3972 \\
VTK marching cubes + gaussian filtering  & 26.6482 \\
ITK BinaryMask3DMeshSource               & 29.1124 \\
 \hline
\end{tabular}\end{center}
\caption{ \label{tab:perf} }
\end{table}
